The client application has to be working on iOS, Android, Microsoft
phone and WEB, there is a ton of Cross Platform Mobile development tools
out there.

For example

\begin{itemize}
\tightlist
\item
  \textbf{Xamarin} - which is the most popular choice, a free trail is
  available and it use the language C\#. This will make it more
  structured as C\# is an \emph{OO} language.
\item
  \textbf{Phone Gap} - which is the most well known tool, it is open
  source meaning that it is free. It uses the common web languages to
  create hybrid apps i.e.~HTML, CSS, JavaScript.
\item
  \textbf{appcelerator} - lets developers use JavaScript to build their
  apps, provide mobile testing, it has a GUI to create design (which
  uses common HTML and CSS), and lastly it is free.
\end{itemize}

There is plenty more but there is one last option that we want to
consider which is to create it only to WEB, the question we need to ask
ourselves is: \emph{are we going to produce a app for the different app
stores or do we only want it to work on the different devices (Android,
iOS, Microsoft phone)?} We will not create an app for the different app
stores out there since that is not in the requirements, because of this
the application will be built using common WEB languages. We will use
responsive design to style our app so it will be desktop, tablet and
mobile friendly. For this we will use a CSS framework, all CSS
frameworks comes also with a JavaScript framework for design purpose
(animation etc.).

CSS frameworks

\begin{itemize}
\tightlist
\item
  \textbf{Bootstrap} - the most common framework out there, easy to use
  and creates fast design. Great for dynamic designing thanks to its
  grid system. The major drawback is that it will look boring and old.
\item
  \textbf{Material Framework} - Google's own framework, a google look
  alike framework.
\item
  \textbf{Semantic UI} - a fresh framework that has grown quite popular
  in the last couple of years. It uses the JavaScript jQuery framework
  which is easy to use and has great AJAX calls which can be helpful.
\end{itemize}

This is only a design option and we will go with the Semantic UI because
it has a suiting design, and for the use of jQuery.

\subparagraph{To summarize}\label{to-summarize}

We will use basic WEB development for our application as the requirement
only says that it should work on iOS, Android etc.\\
The framework that will be in used for WEB development is Semantic UI
for CSS and jQuery for JavaScript as it comes with Semantic UI.
